\documentclass[14pt]{article}

\usepackage[margin=1in]{geometry}

\begin{document}

		\title{THE MUSICIAN's REPORT}
		\author{Author :  LUGADA JOSHUA DAN }
		\date{Student No: 215003299}
		\maketitle
	

	

	\section{Abstract.}
\begin{Large}

	The aim of this report was to investigate how people end up becoming music instrumentalists, how they live and how far music takes them. According to my fellow instrumentalists and observation majority gained the interest of playing while in church and a few through watching others play them. But all these categories of people learn how to play by themselves being driven by the burning passion in their hearts and in just a few months they are good at it. The report concludes that these people are driven by the determination and to get as good as they are its due consistent practice they do.  
 \end{Large}.

	\section{Introduction}
\begin{Large}

	Many instrumentalists including myself, were born without the desire to play instruments but there’s that one day either at the church or club or someplace else where there will be this band playing and the music will just take over your body mind and soul and before you know it you just want to be like those people you’re seeing play. You just fall in love with how them drummer is swinging the sticks in the air, the keyboardist tickling the keys and boom that’s the day you will become one of them.

	Majority of the instrumentalists we have nowadays have not been trained by professionals other than themselves but nevertheless they turned out to be good playing the instruments. Over 70 percent of the instrumentalists today all begun playing in church because most of them this where they get their first experience from and slowly by slowly they start playing even outside church. Some even start writing their own songs and before the know it they have become sounding musicians.

	For purposes of this report, anyone can be a musician or an instrumentalist if they have the time and passion for what they are doing, do as much practice as they can, pay less attention to criticism, listen to as much music as possible then they can become the person they dream to be.
 \end{Large}.
 
	\section{Conclusion}
\begin{Large}	

	Becoming an instrumentalist is not rocket science, it takes one’s determination, attitude, passion and discipline to like that role model they have or even better but becoming an excellent one there is one more aspect of life that you have to supplement on the above and that is creativity. Not only will it make you a star but also a role model to another bunch of fellows.
   \end{Large}.


\end{document}